Are environmental and geographic variables effective surrogates for genetic variation in conservation planning?

### 2016-02-18 article/article.Rmd
+ manuscript edits + switch back to mclust + use less complicated stats

## Introduction
<!--  main text -->
Biodiversity is under threat. In recent history, many species have gone extinct [@r270; @r272]. Today, thousands of species are listed as endangered or near threatened in the International Union for Conservation of Nature (IUCN) red list (\url{www.iucnredlist.org}). In the near future, species are expected to face even more threats [eg. climate change; @r236; @r243]. In response to this crisis, the overarching aim of conservation is to maximize the long-term persistence of biodiversity [@r255; @r67].

Protected areas are one of the hallmarks of modern conservation [@r440]. They buffer species from anthropogenic impacts and provide places for biodiversity processes to persist (eg. nutrient cycling and water purification). Protected areas also set the stage for direct management actions to enhance species recovery (eg. habitat rehabilitation, translocation, and invasive species management). But the resources available for conservation are limited, and so protected areas must be cost-effective. As a consequence, decision support tools [eg. $\texttt{MARXAN}$; @r22; $\texttt{Zonation}$; @r429] are used to identify cost-effective plans for protected areas (prioritizations). These tools typically estimate the benefit that a given species receives from a given prioritization based on the proportion of its range that is secured (eg. using targets). However, the true benefit of a given prioritization is dependent on many additional factors that are not used to inform the reserve selection process.

Protected areas must preserve intra-specific genetic variation to maximize species recovery [@r67; @r3; @r61]. This variation can be classified as either adaptive or neutral [reviewed in @r????]. Adaptive genetic variation is associated with loci currently under selection. By preserving existing patterns of adaptive variation, protected areas can ensure that populations with particularly beneficial adaptations are not lost [@r3]. In contrast, neutral genetic variation is associated with loci that are not under natural selection. Neutral variation often reflects the evolutionary history of different populations. By preserving existing patterns of neutral variation, protected areas can secure different genetic lineages and avoid the adverse effects of low genetic diversity [eg. inbreeding depression; @r67]. However, genetic data requires considerable investment to obtain and analyze. As a consequence, conservation planners do not typically use genetic data to inform prioritizations [@r61]. Thus many prioritizations may fail to capture species' intra-specific genetic variation, and ultimately fail to deliver conservation outcomes.

In light of this problem, conservation scientists have been investigating surrogates for genetic variation to generate better prioritizations--but without the overheads associated with genetic data. Since adaptive genetic variation is ultimately driven by selection pressures, conservation planners have used the distribution of likely selection pressures. For instance, environmental variation such as local habitat type [@r247] and climate [@r2] have been used to guide the reserve selection process. While such variables have been used to detect and verify adaptive genetic variation [eg. @r475; @r455], the effectiveness of prioritizations based on such surrogates remains unverified.

On the other hand, neutral genetic variation arises a reduction in gene flow between individuals. By modeling the connectivity between areas, a function of gene flow, conservation scientists have explored the effectiveness of surrogates for neutral genetic variation. For instance, the isolation by distance theory [IBD; @r259] predicts that populations further apart will have reduced connectivity, and in turn exchange less genetic material. The use of geographic distance-based surrogates has been found to improve prioritizations in an island network [@r200]. However this remains untested in spatially contiguous systems where connectivity is complicated by additional factors [eg. terrain; eg. @r474]--the systems commonly featured in real-world conservation planning exercises. Before conservation planners can reliably use surrogates for genetic data in conservation planning, the effectiveness of these surrogates needs to be verified. Otherwise, if these surrogates are ineffective, conservation planners may waste precious resources on places with little benefit.

Our overarching aim was to investigate the effectiveness of environmental and geographic surrogates for adaptive neutral genetic variation in the context of conservation planning. First, we aimed to understand the relationship between the surrogate targets used to generate a prioritization and the proportion of genetic variation secured in the prioritization. Second, we aimed to determine if the addition of surrogate-based targets in more realistic conservation planning scenarios would result in prioritizations that secured substantially more genetic variation. If these surrogates can be shown to improve the intra-specific genetic variation captured in a prioritization, then conservation planners may use these surrogates when genetic data is not available, and in turn deliver more effective protected areas.

## Methods
### Study system
To address the aims of the study, we utilized species distribution and genomic data collected by the IntraBioDiv project [@r451; see @r452 for methodological details]. This dataset was particularly well suited; it provides spatially explicit genomic data for a multitude of species across a broad geographic area over large environmental gradients. As part of this project, data were collected for 27 alpine plant species were across the European Alps according to a grid (22.3 km $\times$ 25 km; Figure S1). Briefly, in every second cell, plant samples were collected from three individuals for each species present inside the cell. Cells that did not contain any plant samples were omitted from our analysis. Samples were genotyped using amplified fragment length polymorphisms [AFLP; @r453]. Matrices denoting the presence/absence of polymorphisms at loci were constructed independently for each species. Thus for each second grid cell, for each of the species in the grid cell, the dataset contains information describing the genomic variation of individuals inside the grid cell. We used these grid cells as planning units to develop prioritizations to investigate the effectiveness of surrogates for the (AFLP) genetic variation. The majority of our analyses described hereafter were performed using the \texttt{R} software package [version `r paste0(version$major, '.', version$minor)`; @r192].

### Landscape data
We aimed to investigate the effectiveness of climatic and geographic surrogates. To describe the location of each grid cell, we projected the grid into an equi-distant coordinate system ($\texttt{ESRI:102031}$), calculated their centroids, and extracted its two-dimensional coordinates. To describe the climatic variation among each cell, we obtained 19 bioclimatic variables [approx. 1 km resolution; @r33]. These layers and the grid cells were projected into an equal-area coordinate system ($\texttt{ESRI:102014}$). The bioclimatic variables were clipped to the extent of the grid and subject to a principle components analysis (PCA; using ArcMap version 10.2.2; Table S1). The first two principle components (PCs) cumulatively explained `r round(pca.DF[[4]][2],1)` % of the variation and were used to generate two new layers. We calculated the average value for each PC layer in each grid cell, and used these values to characterize the main themes of climatic variation among the grid cells (Figure S2). To examine if the influence of opportunity cost, we calculated the total human population density inside each planning unit (obtained at 1 km resolution from the Global Rural-Urban Mapping Project; GRUMP V1; @r472).

### Outlier locus detection
To investigate the effectiveness of the surrogates for adaptive and neutral genetic variation, we first need to identify which of the sampled loci--if any--were under selection for each species. We used outlier locus detection methods [evaluated in @r454] to achieve this. The basic premise underpinning these analyses is that neutral loci are expected to exhibit a specific level of variation among populations ($F_{st}$), and loci that deviate from this expectation should be under selection. The advantage of these methods--in contrast with environmental association analyses [eg. r@475]--is that they do not use environmental data to identify loci under selection, which would have biased our analysis. In an earlier study, Bothwell _et al._ [-@r455] applied such outlier detection methods to one of the species in this dataset (_Getiana nivalis_). Here, we adopted a similar methodology and applied it to each of the 27 species in the dataset.

First, we grouped individuals into genetic lineages for each species. The purpose of this step was to avoid misclassifying loci as adaptive. We used discriminant analyses of principle components [DAPC; @r467] to assign individuals to populations [implemented in $\texttt{adegenet}$ R package; @r468]. Briefly, for each species, we transformed the binary loci data using a principle components analysis (PCA) and obtained the principle components required to explain at least `r adegenet.params.LST[[MODE]]$perc.pca` % variation. We subject these components to multiple \textit{k}-means clustering models with varying numbers of assumed populations (\textit{k} = 1--`r adegenet.params.LST[[MODE]]$max.n.clust`; `r adegenet.params.LST[[MODE]]$n.iter` iterations; `r adegenet.params.LST[[MODE]]$n.start` random starts). We then  applied Ward's clustering method to the Bayesian Information Criterion (BIC) statistics associated with each model to partition the models into two groups, and selected the model before the first group switch (as recommended in the \texttt{adegenet} manual; Figure S4). The populations memberships associated with these models were used for subsequent analysis (Figure S5).

We identified loci under selection. For each species, we ran $\texttt{Bayescan}$ [version 2.1; @r456] using the population memberships identified in the previous analysis (1:1 prior odds; `r bayescan.params.LST[[MODE]]$nbp` pilot runs; `r bayescan.params.LST[[MODE]]$burn` burn-in iterations; `r bayescan.params.LST[[MODE]]$n` post-burn-in iterations thinned by `r bayescan.params.LST[[MODE]]$thin` iterations; Table S2). To avoid false-positive, we omitted loci where the global frequency of the minor allele was $\geq 0.05$ (following guidelines in the $\texttt{Bayescan}$ manual). We ran `r bayescan.params.LST[[MODE]]$reps` replicates per species using a suitable false discovery rate to ensure convergence [FDR $\leq `r bayescan.params.LST[[MODE]]$fdr`$; @r466].

After classifying loci as adaptive or neutral, we mapped the main gradients of the adaptive (if detected) and neutral genetic variation for each species (Figures S6--S32). For each species, for each type of genetic variation detected, we used Gower distances [@r464] to express the genomic differences between individuals [using the $\texttt{cluster}$ R package to accommodate sparsity; @r457]. These distances were subject to multiple non-metric multi-dimensional scaling analyses [NMDS; implemented in the $\texttt{vegan}$ R package; @r458] using the minimum number of dimensions required to achieve an adequate stress value  ($\leq$ `r nmds.params.LST[[MODE]]$max.stress`; `r nmds.params.LST[[MODE]]$trymax` random starts for all models; Table S3). Since each grid cell had up to three samples per species, we used the average of the ordinated values associated with the samples in each grid cell to summarize the typical genetic characteristics of individuals in the cells.

@@

### Concluding remarks
The overarching aim of our study was to investigate the effectiveness of surrogates in conservation planning. We found that environmental and geographic surrogates are effective. However, they seem to be largely unnecessary in conservation planning scenarios because a comprehensive set of species can be used to achieve a similar result. Conservation planners are therefore urged to use a comprehensive set of species in prioritizations--one of the fundamental principles of conservation planning.

>>>>

## Introduction
<!--  main text -->
The act of setting aside areas for preservation spearheads modern conservation efforts [@r440]. They buffer species from anthropogenic impacts and provide places for populations of species to persist. Intra-specific genetic variation underpins species persistence, and there has been increasing interest in understanding how to design protected areas networks in a way that maximizes this variation [@r67; @r3; @r61]. Broadly speaking, genetic variation can be classified as either adaptive or neutral [reviewed in @r????]. Adaptive genetic variation is associated with loci currently under selection. By preserving existing patterns of adaptive variation, protected areas can ensure that populations with particularly beneficial adaptations are not lost [@r3]. In contrast, neutral genetic variation is associated with loci that are not under natural selection. Neutral variation often reflects the evolutionary history of different populations. By preserving existing patterns of neutral variation, protected areas can secure different genetic lineages and avoid the adverse effects of low genetic diversity [eg. inbreeding depression and reduced capacity to respond to environmental change; @r67]. However, genetic data requires considerable investment to obtain and analyze. As a consequence, conservation planners do not typically use genetic data to inform prioritizations [@r61]. Thus many prioritizations may fail to capture species' intra-specific genetic variation, and ultimately fail to deliver long-term conservation outcomes.

Recently, conservation scientists have been investigating surrogates for genetic variation to generate better prioritizations without the overheads associated with genetic data. Since adaptive genetic variation is ultimately driven by extrinsic selection pressures, environmental variables have been used to guide reserve selection [eg. habitat type and local climate; @r247; @r2]. These variables are often used to detect adaptive variation [eg. @r475; @r455]. However, their effectiveness as surrogates in conservation planning remains unverified. On the other hand, neutral genetic variation arises from a reduction in gene flow between individuals. Thus surrogates for neutral variation are based on variables that predict the level of connectivity between planning units. For instance, the isolation by distance theory [IBD; @259] predicts populations further apart will have less connectivity,  result in reduced gene flow, and in turn share less neutral genetic variation. Geographic distance-based surrogates have been found to improve prioritizations in an island network [@200]. However this remains untested in spatially contiguous systems where connectivity is complicated by additional factors [eg. terrain; eg. @r474]--the systems commonly featured in real-world conservation planning exercises. Before conservation planners can reliably use surrogates for genetic data in conservation planning, the effectiveness of these surrogates needs to be verified. Otherwise, conservation planners may waste precious resources on places that do little to benefit biodiversity..

Here we investigate the effectiveness of environmental and geographic surrogates for adaptive and neutral genetic variation in the context of conservation planning. First, we examine the relationship between surrogates and gene variation, and verify that these variables can be used as surrogates. Second, we determine if the inclusion of surrogate-based targets in a variety of conservation planning scenarios with increasingly levels of realism can result in prioritizations that secure more genetic variation. If these surrogates can be shown to improve the intra-specific genetic variation captured in a prioritization, then conservation planners may use these surrogates when genetic data is not available, and in turn deliver more effective protected areas.

## Methods
### Study system
We used species distribution and genomic data collected by the IntraBioDiv project in the European Alps [@r451; see @r452 and @r478 for methodological details]. This dataset was particularly well suited for this study, because it provides spatially explicit genomic data for multiple species with vastly different demographic characteristics and evolutionary histories across a broad geographic area with large environmental gradients. As part of this project, data was collected for 27 alpine plant species using a 20' longitude by 21' latitude grid (approx. 21' 22.3 km $\times$ 25 km; Figure S1). They visited every second grid cell, and if a species was detected in a grid cell, samples were collected from three individuals. They genotyped samples using amplified fragment length polymorphisms [AFLP; @r453], and constructed matrices denoting the presence/absence of polymorphisms at loci for each species. Thus for each second grid cell, for each of the species present in the grid cell, the dataset contains information describing the genomic variation of individuals in that grid cell. We used these grid cells as planning units to develop prioritizations investigating the effectiveness of surrogates for the (AFLP) genetic variation. Note that we omitted grid cells that did not contain any individuals from our analysis. The majority of our analyses described hereafter were performed using the \texttt{R} software package [version `r paste0(version$major, '.', version$minor)`; @r192].

### Landscape data
We aimed to investigate the effectiveness of climatic and geographic surrogates. To describe the location of each grid cell, we projected the grid into an equi-distant coordinate system ($\texttt{ESRI:102031}$), calculated their centroids, and extracted its two-dimensional coordinates. To describe the climatic variation among each cell, we obtained 19 bioclimatic variables [approx. 1 km resolution; @r33]. These layers and the grid cells were projected into an equal-area coordinate system ($\texttt{ESRI:102014}$). The bioclimatic variables were clipped to the extent of the grid and subject to a principal components analysis (PCA; using ArcMap version 10.2.2; Table S1). The first two principal components (PCs) cumulatively explained `r round(pca.DF[[4]][2],1)` % of the variation and were used to generate two new layers. We calculated the average value for each PC layer in each grid cell, and used these values to characterize the main themes of climatic variation among the grid cells (Figure S2). To examine if the influence of opportunity cost, we calculated the total human population density inside each planning unit (obtained at 1 km resolution from the Global Rural-Urban Mapping Project; \texttt{GRUMP V1}; @r472).

### Outlier locus detection
To investigate the effectiveness of the surrogates for adaptive and neutral genetic variation, we first need to identify which of the sampled loci--if any--were under selection for each species. We used outlier locus detection methods [evaluated in @r454] to achieve this. The basic premise underpinning these analyses is that neutral loci are expected to exhibit a specific level of variation among populations ($F_{st}$), and loci that deviate from this expectation should be under selection. The advantage of these methods--in contrast with environmental association analyses [eg. r@475]--is that they do not use environmental data to identify loci under selection, which would have biased our analysis. In an earlier study, Bothwell _et al._ [-@r455] applied such outlier detection methods to one of the species in this dataset (_Gentiana nivalis_). Here, we adopted a similar methodology and applied it to each of the 27 species in the dataset.

First, we grouped individuals into genetic lineages for each species. The purpose of this step was to avoid misclassifying loci as adaptive. For each species, we used non-metric multi-dimensional scaling [NMDS; implemented in the $\texttt{vegan R}$ package] to transform the binary loci data into continuous variables (Table S2). We used Gower distances [@r464] to express the genomic differences between individuals [using the $\texttt{cluster R}$ package to accommodate sparsity; @r457]. We ran successive scaling analyses with increasing dimensionality until ordinations were obtained with an adequate stress value ($\leq$ `r nmds.params.LST[[MODE]]$max.stress`; `r nmds.params.LST[[MODE]]$trymax` random starts for all models). We then fit a suite of Gaussian mixture to the ordinated values to estimate the probability that individuals belonged to different populations [using the default priors and covariance structures implemented in the $\texttt{mclust} R$ package; @r477; @r476]. For each parametrization, we fit a set of models assuming varying numbers of total populations (\textit{G}= 1--`r max(mclust.params.LST[[MODE]]$G)`). We identified the most parsimonious models (lowest Bayesian Information Criterion $BIC$ statistic; Figures S4), and used these to group individuals into populations (Figure S5).

We identified loci under selection (Table S3). For each species, we ran $\texttt{Bayescan}$ [version 2.1; @r456] using the population memberships identified in the previous analysis (1:1 prior odds; `r bayescan.params.LST[[MODE]]$nbp` pilot runs; `r bayescan.params.LST[[MODE]]$burn` burn-in iterations; `r bayescan.params.LST[[MODE]]$n` post-burn-in iterations thinned by `r bayescan.params.LST[[MODE]]$thin` iterations). To avoid false-positive, we omitted loci where the global frequency of the minor allele was $\geq 0.05$ (following guidelines in the $\texttt{Bayescan}$ manual). We ran `r bayescan.params.LST[[MODE]]$reps` replicates per species using a suitable false discovery rate to ensure convergence [FDR $\leq `r bayescan.params.LST[[MODE]]$fdr`$; @r466].

After classifying loci as adaptive or neutral, we mapped the main gradients of the adaptive (if detected) and neutral genetic variation for each species (Figures S6--S32). For each species, we partitioned adaptive and neutral loci into separate datasets, and reran the nonmetric multidimensional scaling analysis (NMDS) to derive continuous variables that described the main gradients of adaptive and neutral genetic variation separately (Table S2). Since each grid cell had up to three samples per species, we used the average of the ordinated values associated with the individuals in each grid cell to summarize the typical genetic characteristics of individuals in the cells.

@@

### Concluding remarks
The overarching aim of our study was to investigate the effectiveness of surrogates in conservation planning. We found that environmental and geographic surrogates are effective. However, they seem to be largely unnecessary in conservation planning scenarios because a comprehensive set of species can be used to achieve a similar result. Conservation planners are therefore urged to use a comprehensive set of species in prioritizations--one of the fundamental principals of conservation planning.

### 2016-02-18 article/supporting_information.Rmd
+ manuscript edits + switch back to mclust + use less complicated stats

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width=9.5, fig.height=10, fig.cap='Relative support ($BIC$) for the number of populations in each species. Each panel denotes a different species. Asterisks indicate the number of populations with the most support (see text for methodological details).'}
# format data
bic.buff <- laply(spp.Adegenet.LST, `[[`, 'Kstat') %>%
	c() %>% range() %>% diff %>% `*`(0.05)
bic.DF <- ldply(
	seq_along(unique(spp.samples.DF$species)),
	.fun=function(i) {
		data.frame(
			k=as.numeric(gsub('K=', '', names(spp.Adegenet.LST[[i]]$Kstat), fixed=TRUE)),
			stat=unname(spp.Adegenet.LST[[i]]$Kstat),
			best_k=as.numeric(gsub('K=', '', names(spp.Adegenet.LST[[i]]$stat), fixed=TRUE)),
			best_stat=unname(spp.Adegenet.LST[[i]]$stat) + bic.buff,
			asterisk_col=c('black',rep('transparent', length(spp.Adegenet.LST[[i]]$Kstat)-1)),
			Species=gsub('_', ' ', unique(spp.samples.DF$species)[i], fixed=TRUE)
		)
	}
)
# make plot
suppressWarnings({
	ggplot(data=bic.DF) +
		geom_point(aes(y=stat, x=k)) +
		geom_point(aes(y=best_stat, x=best_k), size=4, shape=8) +
		geom_line(aes(y=stat, x=k)) +
		theme_classic() +
		theme(
			strip.background = element_rect(fill='grey20'),
			strip.text = element_text(color='white', face='italic', size=20)
		) +
		xlab('Number of populations') +
		ylab('BIC') +
		facet_wrap(~ Species, ncol=4)
})
```

@@

@@

```{r, echo=FALSE}
knitr::kable(
	format.table(
		filter(
			ldply(
				seq_along(unique(spp.samples.DF$species)), 
				function(i) {
					ldply(
						seq_along(spp.nmds.LST[[i]]),
						function(j) {
						data.frame(
							Species=paste0('\\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[i]),'}'),
							Loci=names(spp.nmds.LST[[i]])[j],
							k=ifelse(is.null(spp.nmds.LST[[i]][[j]]), NA_integer_, spp.nmds.LST[[i]][[j]]$ndim),
							Stress=ifelse(is.null(spp.nmds.LST[[i]][[j]]), NA_real_, spp.nmds.LST[[i]][[j]]$stress),
							Converged=ifelse(is.null(spp.nmds.LST[[i]][[j]]), NA, spp.nmds.LST[[i]][[j]]$converged)
						)
					})
				}
			),
			!is.na(Stress)
		),
		omit=c('Loci','Converged')
	),
	digits=2,
	caption='Summary of non-metric multi-dimensional scaling (MDS) analyses on genetic variation for each species.',
	col.names=c('Species', 'Loci Type', 'k', 'NMDS Stress', 'Converged'),
	align=c('l', 'c', 'c', 'c', 'c')
)
```

>>>>

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width=9.5, fig.height=10, fig.cap='Relative support ($BIC$) for the number of populations in each species. Each panel denotes a different species. Each line denotes a different model parametrization. Asterisks indicate the model and number of populations with the most support.'}
# format data
bic.DF <- ldply(
	seq_along(unique(spp.samples.DF$species)),
	.fun=function(i) {
		curr.MTX <- spp.Mclust.LST[[i]]$mclust$BIC
		attr(curr.MTX, 'dim') <- c(nrow(curr.MTX), ncol(curr.MTX))
		attr(curr.MTX, 'dimnames') <- list(
			seq_len(nrow(curr.MTX)),
			attr(curr.MTX, 'modelNames')
		)
		class(curr.MTX) <- 'matrix'
		curr.DF <- curr.MTX %>% as.data.frame %>% 
			mutate(G=attr(curr.MTX, 'G')) %>% 
			gather(Model,BIC,-G)
		curr.DF$BIC=curr.DF$BIC*-1
		return(
			mutate(
				curr.DF,
				Species=gsub('_', ' ', unique(spp.samples.DF$species)[i], fixed=TRUE),
				best_G=curr.DF[which.min(curr.DF$BIC),'G'][[1]],
				best_stat=min(curr.DF$BIC,na.rm=TRUE),
				asterisk_col=c('black', rep(NA_character_, length(Species)-1))
			)
		)
	}
)
# define ggplot2 color wheel function
gg_color_hue <- function(n) {
	hues <- seq(15, 375, length=n+1)
	hcl(h=hues, l=65, c=100)[1:n]
}
# make plot
suppressWarnings({
	ggplot(data=bic.DF) +
		geom_point(aes(y=BIC, x=G, color=Model)) +
		geom_line(aes(y=BIC, x=G, color=Model)) +
		geom_point(aes(y=best_stat, x=best_G), size=4, shape=8) +
		theme_classic() +
		scale_y_reverse()+
		theme(
			strip.background = element_rect(fill='grey20'),
			strip.text = element_text(color='white', face='italic', size=20)
		) +
		xlab('Number of populations') +
		ylab('BIC') +
		scale_linetype_manual(value=rep(c('solid','dashed'),each=7)) +
		scale_color_manual(value=rep(gg_color_hue(7),2) +
		facet_wrap(~ Species, ncol=4, scales='free_y')
})
```

@@

```{r, echo=FALSE}
knitr::kable(
	format.table(
		filter(
			ldply(
				seq_along(unique(spp.samples.DF$species)), 
				function(i) {
					ldply(
						seq_along(spp.nmds.LST[[i]]),
						function(j) {
						rbind(
							data.frmae(
								Species=paste0('\\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[i]),'}'),
								Loci='all',
								k=spp.Mclust.LST[[i]]$nmds$ndim,
								Stress=spp.Mclust.LST[[i]]$nmds$stress,
								Converged=spp.Mclust.LST[[i]]$nmds$converged
							),
							data.frame(
								Species=paste0('\\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[i]),'}'),
								Loci=names(spp.nmds.LST[[i]])[j],
								k=ifelse(is.null(spp.nmds.LST[[i]][[j]]), NA_integer_, spp.nmds.LST[[i]][[j]]$ndim),
								Stress=ifelse(is.null(spp.nmds.LST[[i]][[j]]), NA_real_, spp.nmds.LST[[i]][[j]]$stress),
								Converged=ifelse(is.null(spp.nmds.LST[[i]][[j]]), NA, spp.nmds.LST[[i]][[j]]$converged)
							)
					})
				}
			),
			!is.na(Stress)
		),
		omit=c('Loci','Converged')
	),
	digits=2,
	caption='Summary of non-metric multi-dimensional scaling (MDS) analyses on genetic variation for each species. The analyses on all loci were used to transform the binary presence/absence polymorphism data to continuous variables to train Gaussian mixture models and ultimately identify adaptive loci. The analyses on adaptive and neutral loci were used to transform the polymorphism data to identify main gradients of this variation.',
	col.names=c('Species', 'Loci Type', 'k', 'NMDS Stress', 'Converged'),
	align=c('l', 'c', 'c', 'c', 'c')
)
```

@@
